A user-friendly tool to evaluate the effectiveness of no-take marine reserves

### 2018-01-18 plostemplate/ManuscriptPLOS.tex
Added changes required by editorial team

Among the biological indicators, the greatest effect of the reserve was observed for snail and sea cucumber densities, with values of \(\beta_2 = 97.17\) (\emph{p} \textless{} 0.05) and \(\beta_2 = 2.31\) (\emph{p} \textless{} 0.05), respectively. Fish indicators showed no significant change (\emph{p} \textgreater{} 0.1), with negative trends for Shannon's diversity index and fish species richness and positive trends for density, biomass, and mean trophic level. Changes through time for these indicators are presented in Figure~\ref{fig5}, and a summary of \(\beta_2\) coefficients is provided in Table~\ref{table3}.

@@

One of the main objectives of this reserve was to increase landings. Results of the socioeconomic indicators show that total landings were, on average, 64.20 metric tonnes higher (\emph{p} \textgreater{} 0.1) after the implementation of the reserves, though this cannot necessarily be interpreted as causal, because it relies entirely on a before-after comparison. Total income was \$10,344.85 (\emph{p} \textless{} 0.05) thousands of Mexican Pesos (K MXP) higher after the implementation of the reserves. On average, lobster and sea cucumber landings increased, while urchin and snail landings and income decreased. Figure~\ref{fig6} presents the changes in these indicators through time, and Table~\ref{table4} summarizes these results.

@@

The causal inference techniques used by MAREA have been suggested \cite{burgess_2018-HN,ferraro_2006-oW} and used \cite{moland_2013-VP} before in other ad hoc studies. This approach reduces ambiguity in the interpretation of results. For example, invertebrate density decreased through time inside and outside of the reserve (Figure~\ref{fig5}h). In this case, a before--after evaluation of the reserve (\emph{i.e.} ignoring the control site) would have incorrectly concluded that the reserve failed to protect invertebrates. On the other hand, a control--impact approach (\emph{i.e.} compare reserve vs.~control site only in 2016) would have identified higher densities inside the reserve, concluding that the reserve increases invertebrate density. However, by executing a formal difference-in-differences approach for causal inference, MAREA identifies the changes through time and across sites, and estimates the effect of the reserve on density at \(\beta_2 = 91.21\) (\emph{p} \textless{} 0.05). This approach reveals that invertebrate densities decrease in both sites through time, but the decrease is faster for the control site, thus yielding a positive value for \(\beta_2\).

@@

\paragraph*{S3 Table}
\label{S3_Table}
{\bf Assigned values and reasoning of socioeconomic and governance indicators used to color-code the scorecard in MAREA}

>>>>

Among the biological indicators, the greatest effect of the reserve was observed for snail and sea cucumber densities, with values of \(\beta_2 = 97.17\) (\emph{p} \textless{} 0.05) and \(\beta_2 = 2.31\) (\emph{p} \textless{} 0.05), respectively. Fish indicators showed no significant change (\emph{p} \textgreater{} 0.1), with negative trends for Shannon's diversity index and fish species richness and positive trends for density, biomass, and mean trophic level. Changes through time for these indicators are presented in Fig~\ref{fig5}, and a summary of \(\beta_2\) coefficients is provided in Table~\ref{table3}.

@@

One of the main objectives of this reserve was to increase landings. Results of the socioeconomic indicators show that total landings were, on average, 64.20 metric tonnes higher (\emph{p} \textgreater{} 0.1) after the implementation of the reserves, though this cannot necessarily be interpreted as causal, because it relies entirely on a before-after comparison. Total income was \$10,344.85 (\emph{p} \textless{} 0.05) thousands of Mexican Pesos (K MXP) higher after the implementation of the reserves. On average, lobster and sea cucumber landings increased, while urchin and snail landings and income decreased. Fig~\ref{fig6} presents the changes in these indicators through time, and Table~\ref{table4} summarizes these results.

@@

The causal inference techniques used by MAREA have been suggested \cite{burgess_2018-HN,ferraro_2006-oW} and used \cite{moland_2013-VP} before in other ad hoc studies. This approach reduces ambiguity in the interpretation of results. For example, invertebrate density decreased through time inside and outside of the reserve (Fig~\ref{fig5}h). In this case, a before--after evaluation of the reserve (\emph{i.e.} ignoring the control site) would have incorrectly concluded that the reserve failed to protect invertebrates. On the other hand, a control--impact approach (\emph{i.e.} compare reserve vs.~control site only in 2016) would have identified higher densities inside the reserve, concluding that the reserve increases invertebrate density. However, by executing a formal difference-in-differences approach for causal inference, MAREA identifies the changes through time and across sites, and estimates the effect of the reserve on density at \(\beta_2 = 91.21\) (\emph{p} \textless{} 0.05). This approach reveals that invertebrate densities decrease in both sites through time, but the decrease is faster for the control site, thus yielding a positive value for \(\beta_2\).

@@

\paragraph*{S1 Table}
\label{S1_Table}
{\bf Assigned values and reasoning of socioeconomic and governance indicators used to color-code the scorecard in MAREA}
